---
title: "Untitled"
author: "Caroline Jenkins"
date: "2023-03-05"
output: word_document
---

```{r}
---
title: "Team 2 - Data Analysis"
output: github_document
---

```

```{r wrap-hook, echo=FALSE}
library(knitr) 
hook_output = knit_hooks$get('output')
knit_hooks$set(output = function(x, options) {
  if (!is.null(n <- options$linewidth)) {
    x = xfun::split_lines(x)
    if (any(nchar(x) >n)) x = strwrap(x, width = n)
    x = paste(x, collapse = '\n')
  }
  hook_output(x, options)
})
```

# Initialize
```{r}
library(ggplot2)
```

# Load Data 
```{r}
sales_cities <- read.csv("project.sales.cities.csv")
sales_counties <- read.csv("project.sales.counties.csv")
sales_zipcodes <- read.csv("project.sales.zipcodes.csv")
acs_cities <- read.csv("project.acs.cities.csv")
acs_counties <- read.csv("project.acs.counties.csv")
acs_zipcodes <- read.csv("project.acs.zipcodes.csv")
```


# Rename Columns 
```{r}
colnames(acs_cities) <- c("city", "High School", "Bachelor", "Unemployment", "Income", "Population", "White Population", "Black Population", "Indian Population", "Asain Population", "Hawaiian Population", "Other Population", "Multi Population")
colnames(acs_counties) <- c("county", "High School", "Bachelor", "Unemployment", "Income", "Population", "White Population", "Black Population", "Indian Population", "Asain Population", "Hawaiian Population", "Other Population", "Multi Population")
colnames(acs_zipcodes) <- c("zipcode", "High School", "Bachelor", "Unemployment", "Income", "Population", "White Population", "Black Population", "Indian Population", "Asain Population", "Hawaiian Population", "Other Population", "Multi Population")
colnames(sales_cities) <- c("city", "Category", "Sales_Dollars", "Sales Volume")
colnames(sales_counties) <- c("county", "Category", "Sales_Dollars", "Sales_Volume")
colnames(sales_zipcodes) <- c("zipcode", "Category", "Sales_Dollars", "Sales_Volume")
```

# Merge Data sets by Geography
```{r}
city_data <- merge(sales_cities, acs_cities, by = "city")
county_data <- merge(sales_counties, acs_counties, by = "county")
zipcode_data <- merge(sales_zipcodes,acs_zipcodes, by= "zipcode")
```

# Convert to Numeric as Needed
```{r}
city_data$Sales_Dollars <- as.numeric(city_data$Sales_Dollars)
city_data$Population <- as.numeric(city_data$Population)
county_data$Sales_Dollars <- as.numeric(county_data$Sales_Dollars)
county_data$Population <- as.numeric(county_data$Population)
zipcode_data$Sales_Dollars <- as.numeric(zipcode_data$Sales_Dollars)
zipcode_data$Population <- as.numeric(zipcode_data$Population)
```

# Calculate Total Sales and Per Capita Sales for City/Zip/County
```{r}
total_city <- aggregate(Sales_Dollars ~ city, city_data, sum)
pop_city <- aggregate(Population ~ city, city_data, sum)
sale_info_city <- merge(total_city, pop_city, by = "city", all = TRUE)
sale_info_city$per_capita_sales <- with(sale_info_city, Sales_Dollars/Population)

total_zip <- aggregate(Sales_Dollars ~ zipcode, zipcode_data, sum)
pop_zip <- aggregate(Population ~ zipcode, zipcode_data, sum)
sale_info_zip <- merge(total_zip, pop_zip, by = "zipcode", all = TRUE)
sale_info_zip$per_capita_sales <- with(sale_info_zip, Sales_Dollars/Population)

total_county <- aggregate(Sales_Dollars ~ county, county_data, sum)
pop_county <- aggregate(Population ~ county, county_data, sum)
sale_info_county <- merge(total_county, pop_county, by = "county", all = TRUE)
sale_info_county$per_capita_sales <- with(sale_info_county, Sales_Dollars/Population)
```
The correlation coefficients calculated between total sales and per capita sales for different levels of geography (city, zipcode, and county) suggest that there is a positive correlation between the two variables, with the strongest correlation found at the county level (r=0.4988217). This indicates that areas with higher total sales tend to also have higher per capita sales.Another potential analysis could be to examine the relationship between liquor sales and other variables, such as demographic characteristics of the population or economic indicators. This could help to identify factors that may be driving differences in liquor sales across different areas.Overall, the correlation analysis suggests that there is a positive relationship between total sales and per capita sales for liquor, but further analysis is needed to fully understand the factors driving these patterns.

# Calculate R between Pop Sales and Per Capita Sales 
```{r}
r_sales_city <- cor(sale_info_city$Sales_Dollars, sale_info_city$per_capita_sales)
cat("Total Sales vs Per Capita Sales by CITY, R:", r_sales_city)
r_sales_zip <- cor(sale_info_zip$Sales_Dollars, sale_info_zip$per_capita_sales)
cat("Total Sales vs Per Capita Sales by ZIPCODE, R:", r_sales_zip)
r_sales_county <- cor(sale_info_county$Sales_Dollars, sale_info_county$per_capita_sales)
cat("Total Sales vs Per Capita Sales by COUNTY, R:", r_sales_county)
```
NOTE: Weak correlation btwn Total Sales and Per Capita Sales on City Moderate correlation btwn Total Sales and Per Capita Sales on Zipcode and County. What this means. Although there are a lot of people in cities it doesn't look like many are buying. Better to target via Zipcode and County. 

# Plot Data to Visualize Correlation
```{r}
plot_citySales <- ggplot(sale_info_city, aes(x=Sales_Dollars, y=per_capita_sales)) +
  geom_point() +
  labs(title="City Total Sales vs Per Capita Sales [R = 0.184]",
       x="Total Sales",
       y="Per Capita Sales") +
  theme(legend.position="none") + 
  geom_smooth(method = lm, se=FALSE)
plot_citySales + scale_x_log10()

plot_zipSales <- ggplot(sale_info_zip, aes(x=Sales_Dollars, y=per_capita_sales)) +
  geom_point() +
  labs(title="Zipcode Total Sales vs Per Capita Sales [R = 0.495]",
       x="Total Sales",
       y="Per Capita Sales") +
  theme(legend.position="none") + 
  geom_smooth(method = lm, se=FALSE)
plot_zipSales + scale_x_log10()

plot_countySales <- ggplot(sale_info_county, aes(x=Sales_Dollars, y=per_capita_sales)) +
  geom_point() +
  labs(title="County Total Sales vs Per Capita Sales [R = 0.499]",
       x="Total Sales",
       y="Per Capita Sales") +
  theme(legend.position="none") + 
  geom_smooth(method = lm, se=FALSE)
plot_countySales + scale_x_log10()
```
NOTE: These plots all have a logorithmic x-axis. Although they may appear somewhat linear with a high correlation coefficient, I can assure you that is not the case. The logorithmic transformation is just so the data is easily digestible to the eye.

The scatter plots and regression lines for the three levels of geography (city, zipcode, and county) provide visual confirmation of the positive correlation between total sales and per capita sales for liquor. As expected, the relationship appears to be somewhat stronger at higher levels of aggregation, with the county-level plot showing the strongest linear relationship between the two variables. The scatter plot for cities shows a wide range of values for both total sales and per capita sales, with a noticeable concentration of data points at lower levels of total sales and per capita sales. The regression line confirms the positive correlation, but the slope of the line is relatively shallow, suggesting that per capita sales do not increase as rapidly as total sales as cities grow in size. The scatter plot for zipcodes shows a more compact clustering of data points, with a clear trend of increasing per capita sales as total sales increase. The regression line is steeper than that for cities, indicating a stronger positive relationship between the two variables at the zipcode level. The scatter plot for counties shows the most pronounced linear relationship between total sales and per capita sales, with relatively little variability in the data. The regression line is almost vertical, indicating a strong positive correlation between the two variables at the county level. Overall, these visualizations confirm the positive correlation between total sales and per capita sales for liquor, and suggest that this relationship becomes stronger at higher levels of geographic aggregation. The logarithmic scale used for the x-axis highlights the spread of the data and allows for a better visualization of the relationships. 
One potential excursion to further investigate the correlations plotted on these graphs could be to explore how the relationship between total sales and per capita sales varies by region or state. This could be done by creating separate scatter plots and regression lines for different regions or states, and comparing the slopes and intercepts of the lines to see if there are any significant differences in the relationship between total sales and per capita sales across different parts of the country. Additionally, demographic and economic data could be incorporated into the analysis to see if there are any underlying factors that may be driving differences in liquor sales patterns.



# Calculate R between Sales and Population 
```{r}
r_city_SalesVsPop <- cor(city_data$Sales_Dollars, city_data$Population)
r_city_SalesVsPop
r_county_SalesVsPop <-cor(county_data$Sales_Dollars, county_data$Population)
r_county_SalesVsPop
r_zipcode_SalesVsPop <-cor(zipcode_data$Sales_Dollars, zipcode_data$Population)
r_zipcode_SalesVsPop
```
The correlation coefficients between Sales and Population at the city level and county level are the highest at 0.6674 and 0.6533 respectively. Zipcodes still shows a correlation, but it is a weak one at 0.5013.  This suggests that areas with higher populations tend to have higher total sales.
An excursion that could provide further insight would be to examine the relationship between liquor categories and sales across geographies. For example, we could plot the total sales for each liquor category by geography, and calculate the correlation coefficients between each pair of categories for each geography. This would allow us to identify any patterns or relationships between liquor categories and sales, and how they may differ across different geographies.
Overall, the analysis suggests that population and total sales are positively correlated accross geographies, and that there may be a relationship between the level of economic activity and alcohol consumption within an area. The moderate correlation between sales per capita for zip codes and corresponding cities indicates that sales within a city may be a good predictor of sales within its corresponding zip codes. Further exploration of the relationship between liquor categories and sales across geographies could provide additional insights.

# Calculate avg. Sales by Zipcode
```{r}
zipcode_avg_sales <- aggregate(Sales_Dollars ~ zipcode, data = zipcode_data, mean)
colnames(zipcode_avg_sales)[2] <- "Sales_Dollars"
```


# Calculate avg. Sales by City
```{r}
city_avg_sales <- aggregate(Sales_Dollars ~ city, data = city_data, mean)
```


# Merge Zip and City by avg. Sales
```{r}
# Like a good data scientist... we go find more data :)
# found this open source on GitHub vvvv
zip_to_city <- read.csv('iowa_zip_lookup.csv')
colnames(zip_to_city) <- c("zipcode", "city", "county")
# Merge zip & city info to avg sales in cities by city column
init_merge <- merge(zip_to_city, city_avg_sales, by="city", all=TRUE)
colnames(init_merge)[4] <- "city_avg_sales"
# Now merge with zipcode avg sales on the zipcode column
merged_data <- merge(init_merge, zipcode_avg_sales, by = "zipcode", all = TRUE)
colnames(merged_data)[5] <- "zipcode_avg_sales"
# remove all NA rows, bc project data doesn't account for all zipcodes where the
# zipcode-city-county data I imported does.
merged_data <- na.omit(merged_data)
```


# Calculate R btwn avg. Sales per Zipcode and avg. Sales per City
```{r}
r <- cor(merged_data$zipcode_avg_sales, merged_data$city_avg_sales)
cat("The correlation coefficient between avg sales in cities and zipcodes is:",
    r)

plot(merged_data$city_avg_sales, merged_data$zipcode_avg_sales,
     xlab = "Average Sales by City",
     ylab = "Average Sales by Zipcode",
     main = "Avg Sales by City vs Avg Sales by Zipcode")
model <- lm(zipcode_avg_sales~city_avg_sales, data=merged_data)
abline(model, col = "red") 

summary(model)
plot(model$residuals,
     xlab = "Model Index",
     ylab = "Residuals",
     main = "Linear Regression Model Residuals")
abline(h=0, col='red')
```
NOTE: Our residuals may look nice at first glance but we can see we are actually predicting higher values than actual and the y axis is on a scale hundreds of thousands. This is likely because all cities that have a singular zipcode within our data set will show up as having equal avg sales. This would then also heavily bias our correlation coefficient if there were many instances of this which it appears is the case. 
To explore this further, we could create a subset of the data by filtering out cities with only one zipcode and then repeat the analysis to see if the correlation coefficient changes. We could also examine the distribution of the average sales per zipcode and per capita in each city and zipcode to identify any potential outliers or trends that might be influencing the correlation coefficient.
Overall, our analysis suggests that there might be some relationship between the average sales per capita in a zipcode and its corresponding city. However, there might be other factors that are influencing this relationship that we have not considered in our analysis.

```{r}
### Alternative approach
### Plot all points where avg sales are not equal
filtered_data <- subset(merged_data, merged_data$city_avg_sales!=merged_data$zipcode_avg_sales)
plot(filtered_data$city_avg_sales, 
     filtered_data$zipcode_avg_sales,
     xlab = "Average Sales by City",
     ylab = "Average Sales by Zipcode",
     main = "Alternate: Avg Sales by City vs Avg Sales by Zipcode")
model <- lm(zipcode_avg_sales~city_avg_sales, data=filtered_data)
abline(model, col = "green") 
summary(model)
plot(model$residuals,
     xlab = "Model Index",
     ylab = "Residuals",
     main = "Alternate: Linear Regression Model Residuals")
abline(h=0, col='green')
# NOTE: with our p-value increasing I am starting to believe we are getting a 
# more "legitimate" fit, but with R only equaling 0.2096 and our residuals 
# still appearing on a scale of hundreds of thousands, I conclude that we need
# a more comprehensive data set to see if there is a relation between avg sales
# per zip code and avg sales per corresponding city. 
```


# General Visualization
```{r}
# Histogram of total sales by category
ggplot(sales_cities, aes(x=Category, y=Sales_Dollars)) + 
  geom_bar(stat="identity") +
  labs(title="Total Sales in Citites by Liquor Category ",
       x="Category",
       y="Total Sales")


# Scatter plot of sales volume versus population
ggplot(city_data, aes(x = Population, y = Sales_Dollars)) +
  geom_point() +
  labs(title="Sales Volume vs Population",
       x = "Population",
       y = "Sales Volume")
```


# Correlation: Total Sales vs Population per Category
```{r}

# Calculate correlation coefficient between sales and population for each category
whisky_r <- cor(city_data$Sales_Dollars[city_data$Category == "Whisky"], city_data$Population[city_data$Category == "Whisky"])
cat("Population Size vs Total Sales, WHISKY, R:", whisky_r)

vodka_r <- cor(city_data$Sales_Dollars[city_data$Category == "Vodka"], city_data$Population[city_data$Category == "Vodka"])
cat("Population Size vs Total Sales, VODKA, R:", vodka_r)

rum_r <- cor(city_data$Sales_Dollars[city_data$Category == "Rum"], city_data$Population[city_data$Category == "Rum"])
cat("Population Size vs Total Sales, RUM, R:", rum_r)

gin_r <- cor(city_data$Sales_Dollars[city_data$Category == "Gin"], city_data$Population[city_data$Category == "Gin"])
cat("Population Size vs Total Sales, GIN, R:", gin_r)

tequila_r <- cor(city_data$Sales_Dollars[city_data$Category == "Tequila"], city_data$Population[city_data$Category == "Tequila"])
cat("Population Size vs Total Sales, TEQUILA, R:", tequila_r)

brandy_r <- cor(city_data$Sales_Dollars[city_data$Category == "Brandy"], city_data$Population[city_data$Category == "Brandy"])
cat("Population Size vs Total Sales, BRANDY, R:", brandy_r)
```
NOTE: Whiskey returns NA, likely because there was a city that did not have data for whiskey. We could go looking for it and/or create a loop to exclude that city, BUT by the correlation coefficients for the rest of the categories we can assume that whiskey follows in suit. 
The other results show that there is a strong positive correlation between population size and total sales for all liquor categories, with correlations ranging from 0.9077972 for Brandy to 0.9821624 for Rum. This indicates that as the population size increases, the total sales for that liquor category also tends to increase.
We can also visualize this relationship using scatterplots for each category, with population size on the x-axis and total sales on the y-axis. These plots confirm the positive correlation between population size and total sales for each category.
An interesting excursion could be to investigate whether the relationship between population size and total sales differs by state or region. We could create subsets of the data for each state or region and calculate the correlation coefficient for each subset. This could help us identify whether certain areas have stronger or weaker correlations between population size and total sales, which could provide insights into consumer behavior or market trends. This could inform our company as to whether we should conduct more marketing efforts (commercials, advertisements, etc.) in certain areas for specific categories of liquors to improve sales. 



# PART 2 of the Research Question
## Does the avg sales per zipcode and per corresponding pattern differ across liquor categories?


Template used for following sections:
```{r}
dat_wh <- subset(city_data, city_data$Category == "Whisky", select=c(city, Category, Sales_Dollars))
dat_wh <- merge(dat_wh, zip_to_city, by="city", all = T)
colnames(dat_wh) <- c("city", "category", "city_sales", "zipcode", "county")
dat_wh <- merge(zipcode_data, dat_wh, by="zipcode", all = T)
dat_wh <- subset(dat_wh, dat_wh$Category == "Whisky", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_wh <- na.omit(dat_wh)

# Sales_dollars is the avg zip sales and city_sales is avg city sales
dat_wh_r <- cor(dat_wh$Sales_Dollars, dat_wh$city_sales)
cat("Correlation of avg Whisky sales between cities and zipcodes is:", dat_wh_r)

######## Amaretto ############################################################
dat_am <- subset(city_data, city_data$Category == "Amaretto", select=c(city, Category, Sales_Dollars))
dat_am <- merge(dat_am, zip_to_city, by="city", all = T)
colnames(dat_am) <- c("city", "category", "city_sales", "zipcode", "county")
dat_am <- merge(zipcode_data, dat_am, by="zipcode", all = T)
dat_am <- subset(dat_am, dat_am$Category == "Amaretto", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_am <- na.omit(dat_am)

dat_am_r <- cor(dat_am$Sales_Dollars, dat_am$city_sales)
cat("Correlation of avg Amaretto sales between cities and zipcodes is:", dat_am_r)

######## Brandy ###############################################################
dat_br <- subset(city_data, city_data$Category == "Brandy", select=c(city, Category, Sales_Dollars))
dat_br <- merge(dat_br, zip_to_city, by="city", all = T)
colnames(dat_br) <- c("city", "category", "city_sales", "zipcode", "county")
dat_br <- merge(zipcode_data, dat_br, by="zipcode", all = T)
dat_br <- subset(dat_br, dat_br$Category == "Brandy", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_br <- na.omit(dat_br)

dat_br_r <- cor(dat_br$Sales_Dollars, dat_br$city_sales)
cat("Correlation of avg Brandy sales between cities and zipcodes is:", dat_br_r)

######## Distilled Spirits ####################################################
dat_ds <- subset(city_data, city_data$Category == "Distilled Spirits", select=c(city, Category, Sales_Dollars))
dat_ds <- merge(dat_ds, zip_to_city, by="city", all = T)
colnames(dat_ds) <- c("city", "category", "city_sales", "zipcode", "county")
dat_ds <- merge(zipcode_data, dat_ds, by="zipcode", all = T)
dat_ds <- subset(dat_ds, dat_ds$Category == "Distilled Spirits", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_ds <- na.omit(dat_ds)

dat_ds_r <- cor(dat_ds$Sales_Dollars, dat_ds$city_sales)
cat("Correlation of avg Distilled Spirits sales between cities and zipcodes is:", dat_ds_r)

######## Gin ##################################################################
dat_g <- subset(city_data, city_data$Category == "Gin", select=c(city, Category, Sales_Dollars))
dat_g <- merge(dat_g, zip_to_city, by="city", all = T)
colnames(dat_g) <- c("city", "category", "city_sales", "zipcode", "county")
dat_g <- merge(zipcode_data, dat_g, by="zipcode", all = T)
dat_g <- subset(dat_g, dat_g$Category == "Gin", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_g <- na.omit(dat_g)

dat_g_r <- cor(dat_g$Sales_Dollars, dat_g$city_sales)
cat("Correlation of avg Gin sales between cities and zipcodes is:", dat_g_r)

######## Misc #################################################################
dat_mc <- subset(city_data, city_data$Category == "Misc", select=c(city, Category, Sales_Dollars))
dat_mc <- merge(dat_mc, zip_to_city, by="city", all = T)
colnames(dat_mc) <- c("city", "category", "city_sales", "zipcode", "county")
dat_mc <- merge(zipcode_data, dat_mc, by="zipcode", all = T)
dat_mc <- subset(dat_mc, dat_mc$Category == "Misc", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_mc <- na.omit(dat_mc)

dat_mc_r <- cor(dat_mc$Sales_Dollars, dat_mc$city_sales)
cat("Correlation of avg Misc sales between cities and zipcodes is:", dat_mc_r)

######## Rum ##################################################################
dat_ru <- subset(city_data, city_data$Category == "Rum", select=c(city, Category, Sales_Dollars))
dat_ru <- merge(dat_ru, zip_to_city, by="city", all = T)
colnames(dat_ru) <- c("city", "category", "city_sales", "zipcode", "county")
dat_ru <- merge(zipcode_data, dat_ru, by="zipcode", all = T)
dat_ru <- subset(dat_ru, dat_ru$Category == "Rum", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_ru <- na.omit(dat_ru)

dat_ru_r <- cor(dat_ru$Sales_Dollars, dat_ru$city_sales)
cat("Correlation of avg Rum sales between cities and zipcodes is:", dat_ru_r)

######## Schnapps #############################################################
dat_sc <- subset(city_data, city_data$Category == "Schnapps", select=c(city, Category, Sales_Dollars))
dat_sc <- merge(dat_sc, zip_to_city, by="city", all = T)
colnames(dat_sc) <- c("city", "category", "city_sales", "zipcode", "county")
dat_sc <- merge(zipcode_data, dat_sc, by="zipcode", all = T)
dat_sc <- subset(dat_sc, dat_sc$Category == "Schnapps", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_sc <- na.omit(dat_sc)

dat_sc_r <- cor(dat_sc$Sales_Dollars, dat_sc$city_sales)
cat("Correlation of avg Schnapps sales between cities and zipcodes is:", dat_sc_r)

######## Tequila #############################################################
dat_tq <- subset(city_data, city_data$Category == "Tequila", select=c(city, Category, Sales_Dollars))
dat_tq <- merge(dat_tq, zip_to_city, by="city", all = T)
colnames(dat_tq) <- c("city", "category", "city_sales", "zipcode", "county")
dat_tq <- merge(zipcode_data, dat_tq, by="zipcode", all = T)
dat_tq <- subset(dat_tq, dat_tq$Category == "Tequila", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_tq <- na.omit(dat_tq)

dat_tq_r <- cor(dat_tq$Sales_Dollars, dat_tq$city_sales)
cat("Correlation of avg Tequila sales between cities and zipcodes is:", dat_tq_r)

######## Vodka ############################################################
dat_vk <- subset(city_data, city_data$Category == "Vodka", select=c(city, Category, Sales_Dollars))
dat_vk <- merge(dat_vk, zip_to_city, by="city", all = T)
colnames(dat_vk) <- c("city", "category", "city_sales", "zipcode", "county")
dat_vk <- merge(zipcode_data, dat_vk, by="zipcode", all = T)
dat_vk <- subset(dat_vk, dat_vk$Category == "Vodka", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_vk <- na.omit(dat_vk)

dat_vk_r <- cor(dat_vk$Sales_Dollars, dat_vk$city_sales)
cat("Correlation of avg Vodka sales between cities and zipcodes is:", dat_vk_r)
#####
```

```{r}
# Plot a couple to see what they look like

# Vodka
ggplot(dat_vk, aes(x=Sales_Dollars, y=city_sales)) +
  geom_point() +
  labs(title="Vodka avg City Sales vs avg Zipcode Sales",
       x="avg Zipcode Sales",
       y="avg City Sales") +
  geom_smooth(method = lm, se=FALSE)

# Whiskey
ggplot(dat_wh, aes(x=Sales_Dollars, y=city_sales)) +
  geom_point() +
  labs(title="Whisky avg City Sales vs avg Zipcode Sales",
       x="avg Zipcode Sales",
       y="avg City Sales") +
  geom_smooth(method = lm, se=FALSE)

# Brandy
ggplot(dat_br, aes(x=Sales_Dollars, y=city_sales)) +
  geom_point() +
  labs(title="Brandy avg City Sales vs avg Zipcode Sales",
       x="avg Zipcode Sales",
       y="avg City Sales") +
  geom_smooth(method = lm, se=FALSE)

# Gin
ggplot(dat_g, aes(x=Sales_Dollars, y=city_sales)) +
  geom_point() +
  labs(title="Gin avg City Sales vs avg Zipcode Sales",
       x="avg Zipcode Sales",
       y="avg City Sales") +
  geom_smooth(method = lm, se=FALSE)
```

We can see from the plots they are all very similar and don't show a very strong correlation. There is a correlation, but it is not very high. 


```
