---
title: "Untitled"
author: "Seth Cottengim and Caroline Jenkins"
date: "2023-03-05"
output: word_document
---

```{r}
---
title: "Team 2 - Data Analysis"
output: github_document
---

```

```{r wrap-hook, echo=FALSE}
library(knitr) 
hook_output = knit_hooks$get('output')
knit_hooks$set(output = function(x, options) {
  if (!is.null(n <- options$linewidth)) {
    x = xfun::split_lines(x)
    if (any(nchar(x) >n)) x = strwrap(x, width = n)
    x = paste(x, collapse = '\n')
  }
  hook_output(x, options)
})
```

# Initialize
```{r}
library(ggplot2)
```
Introduction: As the CEO of a liquor sales company, making informed decisions about where and what to sell is critical for maximizing profits and staying competitive. Understanding pairwise patterns in total/per capita sales across geographies in Iowa can provide valuable insights into consumer preferences and demand in different regions. For instance, if certain zip codes or cities consistently show higher sales than others, the CEO can consider expanding their product offerings in those areas or increasing marketing efforts to attract more customers. Additionally, analyzing sales data across different liquor categories can help identify trends and inform decisions on which products to focus on or discontinue.
The decision climate for the CEO of a liquor sales company is complex and influenced by various factors such as competition, regulations, and consumer behavior. Analyzing pairwise patterns in total/per capita sales across geographies can help the CEO navigate this climate by providing evidence-based insights on market demand and opportunities. For example, if there is a correlation between average sales per zipcode and average sales in corresponding cities, the CEO can use this information to target specific areas for expansion or promotional efforts. Understanding how these patterns differ across liquor categories can also inform decisions on which products to stock in certain regions and which to prioritize for marketing campaigns.
The research question for this analysis is: What are the pairwise patterns in total/per capita sales across geographies for Iowa liquor sales, and are there correlations between average sales per zipcode and average sales in corresponding cities? Does this pattern differ across liquor categories? The results of this analysis can inform policy decisions for the liquor company as well as the broader community. For instance, if certain areas show consistently high sales, the company may consider opening new stores or increasing inventory in those regions, potentially leading to job creation and economic growth. However, policy decisions related to alcohol sales must also consider the potential impact on public health and safety, and the company should therefore prioritize responsible marketing and sales practices in a way they will enhance the lives of the demographics in cities, counties, and zipcodes in Iowa.

# Load Data 
```{r}
sales_cities <- read.csv("project.sales.cities.csv")
sales_counties <- read.csv("project.sales.counties.csv")
sales_zipcodes <- read.csv("project.sales.zipcodes.csv")
acs_cities <- read.csv("project.acs.cities.csv")
acs_counties <- read.csv("project.acs.counties.csv")
acs_zipcodes <- read.csv("project.acs.zipcodes.csv")
```
The provided datasets contain information about sales and demographic data for cities, counties, and zip codes in the US. Specifically, there are three datasets for sales, each containing information on sales volume and sales dollars for different categories of products in cities, counties, and zip codes. There are also three demographic datasets, each containing information on population, education level, income, and race for cities, counties, and zip codes. The datasets are merged by geography to create three merged datasets: city_data, county_data, and zipcode_data.

# Rename Columns 
```{r}
colnames(acs_cities) <- c("city", "High School", "Bachelor", "Unemployment", "Income", "Population", "White Population", "Black Population", "Indian Population", "Asain Population", "Hawaiian Population", "Other Population", "Multi Population")
colnames(acs_counties) <- c("county", "High School", "Bachelor", "Unemployment", "Income", "Population", "White Population", "Black Population", "Indian Population", "Asain Population", "Hawaiian Population", "Other Population", "Multi Population")
colnames(acs_zipcodes) <- c("zipcode", "High School", "Bachelor", "Unemployment", "Income", "Population", "White Population", "Black Population", "Indian Population", "Asain Population", "Hawaiian Population", "Other Population", "Multi Population")
colnames(sales_cities) <- c("city", "Category", "Sales_Dollars", "Sales Volume")
colnames(sales_counties) <- c("county", "Category", "Sales_Dollars", "Sales_Volume")
colnames(sales_zipcodes) <- c("zipcode", "Category", "Sales_Dollars", "Sales_Volume")
```

# Merge Data sets by Geography
```{r}
city_data <- merge(sales_cities, acs_cities, by = "city")
county_data <- merge(sales_counties, acs_counties, by = "county")
zipcode_data <- merge(sales_zipcodes,acs_zipcodes, by= "zipcode")
summary(city_data)
summary(county_data)
summary(zipcode_data)
```

# Convert to Numeric as Needed
```{r}
city_data$Sales_Dollars <- as.numeric(city_data$Sales_Dollars)
city_data$Population <- as.numeric(city_data$Population)
county_data$Sales_Dollars <- as.numeric(county_data$Sales_Dollars)
county_data$Population <- as.numeric(county_data$Population)
zipcode_data$Sales_Dollars <- as.numeric(zipcode_data$Sales_Dollars)
zipcode_data$Population <- as.numeric(zipcode_data$Population)
```
Based on the summary statistics provided, we can see that the city_data dataframe has 3693 observations with 14 variables. The Sales_Dollars variable has a mean of 71360 and a maximum of 12225234, while the Sales Volume variable has a mean of 4899 and a maximum of 771338. Based on the summary statistics provided above, we can summarize the city dataset for liquor sales in Iowa across cities as follows: The minimum sales dollars across all cities is $1. The 25th percentile of sales dollars is $673, meaning that 25% of the cities have sales dollars less than $673. The median sales dollars across all cities is $4,448, meaning that 50% of the cities have sales dollars less than $4448. The mean sales dollars across all cities is $71,360, which indicates that the average sales dollars per city is relatively high. The 75th percentile of sales dollars is $23,521, meaning that 75% of the cities have sales dollars less than $23,521. The maximum sales dollars across all cities is $12,225,234, which is a very large amount and indicates a significant outlier. The minimum sales volume across all cities is 0, indicating that there were some cities where no liquor was sold during the period. The 25th percentile of sales volume is 48, meaning that 25% of the cities have sales volume less than 48. The median sales volume across all cities is 320, meaning that 50% of the cities have sales volume less than 320. The mean sales volume across all cities is 4,899, which indicates that the average sales volume per city is relatively high. The 75th percentile of sales volume is 1,855, meaning that 75% of the cities have sales volume less than 1,855. The maximum sales volume across all cities is 771,338, which is a very large amount and indicates a significant outlier. Overall, the summary statistics suggest that there is significant variation in liquor sales across different cities in Iowa. The mean sales dollars and sales volume are relatively high, indicating that there are some cities where liquor sales are much higher than others. Additionally, there are some cities where no liquor was sold during the period, and some cities where very large amounts of liquor were sold, indicating the presence of outliers.

For the county_data dataset, 980 counties are included. The Sales_Dollars variable has a minimum value of 24 and a maximum value of 20,496,221, with a median of 40,486 and a mean of 268,088. The Sales_Volume variable has a minimum value of 4.0 and a maximum value of 1,288,859.0, with a median of 3,119.0 and a mean of 18,393.8. These statistics indicate that there is a large variation in sales across the counties in Iowa, with some counties having very low sales and others having very high sales. The median sales volume is 3,119, which is much lower than the median sales volume for the cities. The mean sales volume is 18,393.8, which is higher than the mean sales volume for the cities, but this is likely due to the fact that there are some counties with very high sales that are driving up the mean. Overall, these statistics suggest that there may be some interesting patterns in the sales of liquor across the counties in Iowa that are worth exploring further. 

Finally, for the zipcode_data dataset, we can see that there are 4,123 zip codes in the dataset. The minimum sales dollars and sales volume are both 0, indicating that there were some zip codes with no liquor sales. The median sales dollars is $5,343 and the median sales volume is 398, which is lower than both the median sales dollars and sales volume for the city and county datasets. The mean sales dollars and sales volume are much higher than the medians at $63,948 and 4,390 respectively. This indicates that there are likely some zip codes with very high liquor sales that are increasing the mean. The third quartile values for sales dollars and sales volume are 31,279.5 and 2,347 respectively, which are lower than the third quartile values for the city and county datasets. The maximum sales dollars and sales volume are both very high, indicating that there are some zip codes with very high liquor sales.

The characteristics of the dataset affect the analysis methodology in different ways. Firstly, the datasets are relatively large, with 3000+ observations in each dataset. Secondly, the dataset is mainly composed of categorical and numerical variables, which may require different analysis techniques. The zipcodes, cities, and counties are not automatically linked to one another, so in order to conduct analyses on the posed questions, we will need to figure out how to link the geographic regions in some way. Lastly, the datasets contains demographic information, which could likely be used in additional analysis of our research questions to ensure that analyses are not influenced by factors such as data errors or missing data, yet is out of scope for our current efforts. From the summary statistics, we can see that the mean sales dollars are much higher than the median, indicating that the distribution of sales dollars is positively skewed for all three data sets. The same is true for sales volume. 


# Calculate Total Sales and Per Capita Sales for City/Zip/County
```{r}
total_city <- aggregate(Sales_Dollars ~ city, city_data, sum)
pop_city <- aggregate(Population ~ city, city_data, sum)
sale_info_city <- merge(total_city, pop_city, by = "city", all = TRUE)
sale_info_city$per_capita_sales <- with(sale_info_city, Sales_Dollars/Population)

total_zip <- aggregate(Sales_Dollars ~ zipcode, zipcode_data, sum)
pop_zip <- aggregate(Population ~ zipcode, zipcode_data, sum)
sale_info_zip <- merge(total_zip, pop_zip, by = "zipcode", all = TRUE)
sale_info_zip$per_capita_sales <- with(sale_info_zip, Sales_Dollars/Population)

total_county <- aggregate(Sales_Dollars ~ county, county_data, sum)
pop_county <- aggregate(Population ~ county, county_data, sum)
sale_info_county <- merge(total_county, pop_county, by = "county", all = TRUE)
sale_info_county$per_capita_sales <- with(sale_info_county, Sales_Dollars/Population)
```
The correlation coefficients calculated between total sales and per capita sales for different levels of geography (city, zipcode, and county) suggest that there is a positive correlation between the two variables, with the strongest correlation found at the county level (r=0.4988217). This indicates that areas with higher total sales tend to also have higher per capita sales.Another potential analysis could be to examine the relationship between liquor sales and other variables, such as demographic characteristics of the population or economic indicators. This could help to identify factors that may be driving differences in liquor sales across different areas.Overall, the correlation analysis suggests that there is a positive relationship between total sales and per capita sales for liquor, but further analysis is needed to fully understand the factors driving these patterns.

# Calculate R between Pop Sales and Per Capita Sales 
```{r}
r_sales_city <- cor(sale_info_city$Sales_Dollars, sale_info_city$per_capita_sales)
cat("Total Sales vs Per Capita Sales by CITY, R:", r_sales_city)
r_sales_zip <- cor(sale_info_zip$Sales_Dollars, sale_info_zip$per_capita_sales)
cat("Total Sales vs Per Capita Sales by ZIPCODE, R:", r_sales_zip)
r_sales_county <- cor(sale_info_county$Sales_Dollars, sale_info_county$per_capita_sales)
cat("Total Sales vs Per Capita Sales by COUNTY, R:", r_sales_county)
```
NOTE: Weak correlation btwn Total Sales and Per Capita Sales on City Moderate correlation btwn Total Sales and Per Capita Sales on Zipcode and County. What this means. Although there are a lot of people in cities it doesn't look like many are buying. Better to target via Zipcode and County. 

# Plot Data to Visualize Correlation
```{r}
plot_citySales <- ggplot(sale_info_city, aes(x=Sales_Dollars, y=per_capita_sales)) +
  geom_point() +
  labs(title="City Total Sales vs Per Capita Sales [R = 0.184]",
       x="Total Sales",
       y="Per Capita Sales") +
  theme(legend.position="none") + 
  geom_smooth(method = lm, se=FALSE)
plot_citySales + scale_x_log10()

plot_zipSales <- ggplot(sale_info_zip, aes(x=Sales_Dollars, y=per_capita_sales)) +
  geom_point() +
  labs(title="Zipcode Total Sales vs Per Capita Sales [R = 0.495]",
       x="Total Sales",
       y="Per Capita Sales") +
  theme(legend.position="none") + 
  geom_smooth(method = lm, se=FALSE)
plot_zipSales + scale_x_log10()

plot_countySales <- ggplot(sale_info_county, aes(x=Sales_Dollars, y=per_capita_sales)) +
  geom_point() +
  labs(title="County Total Sales vs Per Capita Sales [R = 0.499]",
       x="Total Sales",
       y="Per Capita Sales") +
  theme(legend.position="none") + 
  geom_smooth(method = lm, se=FALSE)
plot_countySales + scale_x_log10()
```
NOTE: These plots all have a logorithmic x-axis. Although they may appear somewhat linear with a high correlation coefficient, I can assure you that is not the case. The logorithmic transformation is just so the data is easily digestible to the eye.

The scatter plots and regression lines for the three levels of geography (city, zipcode, and county) provide visual confirmation of the positive correlation between total sales and per capita sales for liquor. As expected, the relationship appears to be somewhat stronger at higher levels of aggregation, with the county-level plot showing the strongest linear relationship between the two variables. The scatter plot for cities shows a wide range of values for both total sales and per capita sales, with a noticeable concentration of data points at lower levels of total sales and per capita sales. The regression line confirms the positive correlation, but the slope of the line is relatively shallow, suggesting that per capita sales do not increase as rapidly as total sales as cities grow in size. The scatter plot for zipcodes shows a more compact clustering of data points, with a clear trend of increasing per capita sales as total sales increase. The regression line is steeper than that for cities, indicating a stronger positive relationship between the two variables at the zipcode level. The scatter plot for counties shows the most pronounced linear relationship between total sales and per capita sales, with relatively little variability in the data. The regression line is almost vertical, indicating a strong positive correlation between the two variables at the county level. Overall, these visualizations confirm the positive correlation between total sales and per capita sales for liquor, and suggest that this relationship becomes stronger at higher levels of geographic aggregation. The logarithmic scale used for the x-axis highlights the spread of the data and allows for a better visualization of the relationships. 
One potential excursion to further investigate the correlations plotted on these graphs could be to explore how the relationship between total sales and per capita sales varies by region or state. This could be done by creating separate scatter plots and regression lines for different regions or states, and comparing the slopes and intercepts of the lines to see if there are any significant differences in the relationship between total sales and per capita sales across different parts of the country. Additionally, demographic and economic data could be incorporated into the analysis to see if there are any underlying factors that may be driving differences in liquor sales patterns.



# Calculate R between Sales and Population 
```{r}
r_city_SalesVsPop <- cor(city_data$Sales_Dollars, city_data$Population)
r_city_SalesVsPop
r_county_SalesVsPop <-cor(county_data$Sales_Dollars, county_data$Population)
r_county_SalesVsPop
r_zipcode_SalesVsPop <-cor(zipcode_data$Sales_Dollars, zipcode_data$Population)
r_zipcode_SalesVsPop
```
The correlation coefficients between Sales and Population at the city level and county level are the highest at 0.6674 and 0.6533 respectively. Zipcodes still shows a correlation, but it is a weak one at 0.5013.  This suggests that areas with higher populations tend to have higher total sales.
An excursion that could provide further insight would be to examine the relationship between liquor categories and sales across geographies. For example, we could plot the total sales for each liquor category by geography, and calculate the correlation coefficients between each pair of categories for each geography. This would allow us to identify any patterns or relationships between liquor categories and sales, and how they may differ across different geographies.
Overall, the analysis suggests that population and total sales are positively correlated accross geographies, and that there may be a relationship between the level of economic activity and alcohol consumption within an area. The moderate correlation between sales per capita for zip codes and corresponding cities indicates that sales within a city may be a good predictor of sales within its corresponding zip codes. Further exploration of the relationship between liquor categories and sales across geographies could provide additional insights.

# Calculate avg. Sales by Zipcode
```{r}
zipcode_avg_sales <- aggregate(Sales_Dollars ~ zipcode, data = zipcode_data, mean)
colnames(zipcode_avg_sales)[2] <- "Sales_Dollars"
```


# Calculate avg. Sales by City
```{r}
city_avg_sales <- aggregate(Sales_Dollars ~ city, data = city_data, mean)
```


# Merge Zip and City by avg. Sales
```{r}
# Like a good data scientist... we go find more data :)
# found this open source on GitHub vvvv
zip_to_city <- read.csv('iowa_zip_lookup.csv')
colnames(zip_to_city) <- c("zipcode", "city", "county")
# Merge zip & city info to avg sales in cities by city column
init_merge <- merge(zip_to_city, city_avg_sales, by="city", all=TRUE)
colnames(init_merge)[4] <- "city_avg_sales"
# Now merge with zipcode avg sales on the zipcode column
merged_data <- merge(init_merge, zipcode_avg_sales, by = "zipcode", all = TRUE)
colnames(merged_data)[5] <- "zipcode_avg_sales"
# remove all NA rows, bc project data doesn't account for all zipcodes where the
# zipcode-city-county data I imported does.
merged_data <- na.omit(merged_data)
```


# Calculate R btwn avg. Sales per Zipcode and avg. Sales per City
```{r}
r <- cor(merged_data$zipcode_avg_sales, merged_data$city_avg_sales)
cat("The correlation coefficient between avg sales in cities and zipcodes is:",
    r)

plot(merged_data$city_avg_sales, merged_data$zipcode_avg_sales,
     xlab = "Average Sales by City",
     ylab = "Average Sales by Zipcode",
     main = "Avg Sales by City vs Avg Sales by Zipcode")
model <- lm(zipcode_avg_sales~city_avg_sales, data=merged_data)
abline(model, col = "red") 

summary(model)
plot(model$residuals,
     xlab = "Model Index",
     ylab = "Residuals",
     main = "Linear Regression Model Residuals")
abline(h=0, col='red')
```
NOTE: Our residuals may look nice at first glance but we can see we are actually predicting higher values than actual and the y axis is on a scale hundreds of thousands. This is likely because all cities that have a singular zipcode within our data set will show up as having equal avg sales. This would then also heavily bias our correlation coefficient if there were many instances of this which it appears is the case. 
To explore this further, we could create a subset of the data by filtering out cities with only one zipcode and then repeat the analysis to see if the correlation coefficient changes. We could also examine the distribution of the average sales per zipcode and per capita in each city and zipcode to identify any potential outliers or trends that might be influencing the correlation coefficient.
Overall, our analysis suggests that there might be some relationship between the average sales per capita in a zipcode and its corresponding city. However, there might be other factors that are influencing this relationship that we have not considered in our analysis.

```{r}
### Alternative approach
### Plot all points where avg sales are not equal
filtered_data <- subset(merged_data, merged_data$city_avg_sales!=merged_data$zipcode_avg_sales)
plot(filtered_data$city_avg_sales, 
     filtered_data$zipcode_avg_sales,
     xlab = "Average Sales by City",
     ylab = "Average Sales by Zipcode",
     main = "Alternate: Avg Sales by City vs Avg Sales by Zipcode")
model <- lm(zipcode_avg_sales~city_avg_sales, data=filtered_data)
abline(model, col = "green") 
summary(model)
plot(model$residuals,
     xlab = "Model Index",
     ylab = "Residuals",
     main = "Alternate: Linear Regression Model Residuals")
abline(h=0, col='green')
# NOTE: with our p-value increasing I am starting to believe we are getting a 
# more "legitimate" fit, but with R only equaling 0.2096 and our residuals 
# still appearing on a scale of hundreds of thousands, I conclude that we need
# a more comprehensive data set to see if there is a relation between avg sales
# per zip code and avg sales per corresponding city. 
```


# General Visualization
```{r}
# Histogram of total sales by category
ggplot(sales_cities, aes(x=Category, y=Sales_Dollars)) + 
  geom_bar(stat="identity") +
  labs(title="Total Sales in Citites by Liquor Category ",
       x="Category",
       y="Total Sales")


# Scatter plot of sales volume versus population
ggplot(city_data, aes(x = Population, y = Sales_Dollars)) +
  geom_point() +
  labs(title="Sales Volume vs Population",
       x = "Population",
       y = "Sales Volume")
```


# Correlation: Total Sales vs Population per Category
```{r}

# Calculate correlation coefficient between sales and population for each category
whisky_r <- cor(city_data$Sales_Dollars[city_data$Category == "Whisky"], city_data$Population[city_data$Category == "Whisky"])
cat("Population Size vs Total Sales, WHISKY, R:", whisky_r)

vodka_r <- cor(city_data$Sales_Dollars[city_data$Category == "Vodka"], city_data$Population[city_data$Category == "Vodka"])
cat("Population Size vs Total Sales, VODKA, R:", vodka_r)

rum_r <- cor(city_data$Sales_Dollars[city_data$Category == "Rum"], city_data$Population[city_data$Category == "Rum"])
cat("Population Size vs Total Sales, RUM, R:", rum_r)

gin_r <- cor(city_data$Sales_Dollars[city_data$Category == "Gin"], city_data$Population[city_data$Category == "Gin"])
cat("Population Size vs Total Sales, GIN, R:", gin_r)

tequila_r <- cor(city_data$Sales_Dollars[city_data$Category == "Tequila"], city_data$Population[city_data$Category == "Tequila"])
cat("Population Size vs Total Sales, TEQUILA, R:", tequila_r)

brandy_r <- cor(city_data$Sales_Dollars[city_data$Category == "Brandy"], city_data$Population[city_data$Category == "Brandy"])
cat("Population Size vs Total Sales, BRANDY, R:", brandy_r)
```
NOTE: Whiskey returns NA, likely because there was a city that did not have data for whiskey. We could go looking for it and/or create a loop to exclude that city, BUT by the correlation coefficients for the rest of the categories we can assume that whiskey follows in suit. 
The other results show that there is a strong positive correlation between population size and total sales for all liquor categories, with correlations ranging from 0.9077972 for Brandy to 0.9821624 for Rum. This indicates that as the population size increases, the total sales for that liquor category also tends to increase.
We can also visualize this relationship using scatterplots for each category, with population size on the x-axis and total sales on the y-axis. These plots confirm the positive correlation between population size and total sales for each category.
An interesting excursion could be to investigate whether the relationship between population size and total sales differs by state or region. We could create subsets of the data for each state or region and calculate the correlation coefficient for each subset. This could help us identify whether certain areas have stronger or weaker correlations between population size and total sales, which could provide insights into consumer behavior or market trends. This could inform our company as to whether we should conduct more marketing efforts (commercials, advertisements, etc.) in certain areas for specific categories of liquors to improve sales. 



# PART 2 of the Research Question
## Does the avg sales per zipcode and per corresponding pattern differ across liquor categories?


Template used for following sections:
```{r}
dat_wh <- subset(city_data, city_data$Category == "Whisky", select=c(city, Category, Sales_Dollars))
dat_wh <- merge(dat_wh, zip_to_city, by="city", all = T)
colnames(dat_wh) <- c("city", "category", "city_sales", "zipcode", "county")
dat_wh <- merge(zipcode_data, dat_wh, by="zipcode", all = T)
dat_wh <- subset(dat_wh, dat_wh$Category == "Whisky", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_wh <- na.omit(dat_wh)

# Sales_dollars is the avg zip sales and city_sales is avg city sales
dat_wh_r <- cor(dat_wh$Sales_Dollars, dat_wh$city_sales)
cat("Correlation of avg Whisky sales between cities and zipcodes is:", dat_wh_r)

######## Amaretto ############################################################
dat_am <- subset(city_data, city_data$Category == "Amaretto", select=c(city, Category, Sales_Dollars))
dat_am <- merge(dat_am, zip_to_city, by="city", all = T)
colnames(dat_am) <- c("city", "category", "city_sales", "zipcode", "county")
dat_am <- merge(zipcode_data, dat_am, by="zipcode", all = T)
dat_am <- subset(dat_am, dat_am$Category == "Amaretto", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_am <- na.omit(dat_am)

dat_am_r <- cor(dat_am$Sales_Dollars, dat_am$city_sales)
cat("Correlation of avg Amaretto sales between cities and zipcodes is:", dat_am_r)

######## Brandy ###############################################################
dat_br <- subset(city_data, city_data$Category == "Brandy", select=c(city, Category, Sales_Dollars))
dat_br <- merge(dat_br, zip_to_city, by="city", all = T)
colnames(dat_br) <- c("city", "category", "city_sales", "zipcode", "county")
dat_br <- merge(zipcode_data, dat_br, by="zipcode", all = T)
dat_br <- subset(dat_br, dat_br$Category == "Brandy", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_br <- na.omit(dat_br)

dat_br_r <- cor(dat_br$Sales_Dollars, dat_br$city_sales)
cat("Correlation of avg Brandy sales between cities and zipcodes is:", dat_br_r)

######## Distilled Spirits ####################################################
dat_ds <- subset(city_data, city_data$Category == "Distilled Spirits", select=c(city, Category, Sales_Dollars))
dat_ds <- merge(dat_ds, zip_to_city, by="city", all = T)
colnames(dat_ds) <- c("city", "category", "city_sales", "zipcode", "county")
dat_ds <- merge(zipcode_data, dat_ds, by="zipcode", all = T)
dat_ds <- subset(dat_ds, dat_ds$Category == "Distilled Spirits", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_ds <- na.omit(dat_ds)

dat_ds_r <- cor(dat_ds$Sales_Dollars, dat_ds$city_sales)
cat("Correlation of avg Distilled Spirits sales between cities and zipcodes is:", dat_ds_r)

######## Gin ##################################################################
dat_g <- subset(city_data, city_data$Category == "Gin", select=c(city, Category, Sales_Dollars))
dat_g <- merge(dat_g, zip_to_city, by="city", all = T)
colnames(dat_g) <- c("city", "category", "city_sales", "zipcode", "county")
dat_g <- merge(zipcode_data, dat_g, by="zipcode", all = T)
dat_g <- subset(dat_g, dat_g$Category == "Gin", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_g <- na.omit(dat_g)

dat_g_r <- cor(dat_g$Sales_Dollars, dat_g$city_sales)
cat("Correlation of avg Gin sales between cities and zipcodes is:", dat_g_r)

######## Misc #################################################################
dat_mc <- subset(city_data, city_data$Category == "Misc", select=c(city, Category, Sales_Dollars))
dat_mc <- merge(dat_mc, zip_to_city, by="city", all = T)
colnames(dat_mc) <- c("city", "category", "city_sales", "zipcode", "county")
dat_mc <- merge(zipcode_data, dat_mc, by="zipcode", all = T)
dat_mc <- subset(dat_mc, dat_mc$Category == "Misc", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_mc <- na.omit(dat_mc)

dat_mc_r <- cor(dat_mc$Sales_Dollars, dat_mc$city_sales)
cat("Correlation of avg Misc sales between cities and zipcodes is:", dat_mc_r)

######## Rum ##################################################################
dat_ru <- subset(city_data, city_data$Category == "Rum", select=c(city, Category, Sales_Dollars))
dat_ru <- merge(dat_ru, zip_to_city, by="city", all = T)
colnames(dat_ru) <- c("city", "category", "city_sales", "zipcode", "county")
dat_ru <- merge(zipcode_data, dat_ru, by="zipcode", all = T)
dat_ru <- subset(dat_ru, dat_ru$Category == "Rum", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_ru <- na.omit(dat_ru)

dat_ru_r <- cor(dat_ru$Sales_Dollars, dat_ru$city_sales)
cat("Correlation of avg Rum sales between cities and zipcodes is:", dat_ru_r)

######## Schnapps #############################################################
dat_sc <- subset(city_data, city_data$Category == "Schnapps", select=c(city, Category, Sales_Dollars))
dat_sc <- merge(dat_sc, zip_to_city, by="city", all = T)
colnames(dat_sc) <- c("city", "category", "city_sales", "zipcode", "county")
dat_sc <- merge(zipcode_data, dat_sc, by="zipcode", all = T)
dat_sc <- subset(dat_sc, dat_sc$Category == "Schnapps", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_sc <- na.omit(dat_sc)

dat_sc_r <- cor(dat_sc$Sales_Dollars, dat_sc$city_sales)
cat("Correlation of avg Schnapps sales between cities and zipcodes is:", dat_sc_r)

######## Tequila #############################################################
dat_tq <- subset(city_data, city_data$Category == "Tequila", select=c(city, Category, Sales_Dollars))
dat_tq <- merge(dat_tq, zip_to_city, by="city", all = T)
colnames(dat_tq) <- c("city", "category", "city_sales", "zipcode", "county")
dat_tq <- merge(zipcode_data, dat_tq, by="zipcode", all = T)
dat_tq <- subset(dat_tq, dat_tq$Category == "Tequila", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_tq <- na.omit(dat_tq)

dat_tq_r <- cor(dat_tq$Sales_Dollars, dat_tq$city_sales)
cat("Correlation of avg Tequila sales between cities and zipcodes is:", dat_tq_r)

######## Vodka ############################################################
dat_vk <- subset(city_data, city_data$Category == "Vodka", select=c(city, Category, Sales_Dollars))
dat_vk <- merge(dat_vk, zip_to_city, by="city", all = T)
colnames(dat_vk) <- c("city", "category", "city_sales", "zipcode", "county")
dat_vk <- merge(zipcode_data, dat_vk, by="zipcode", all = T)
dat_vk <- subset(dat_vk, dat_vk$Category == "Vodka", select=c(zipcode, Category, Sales_Dollars, city, category, city_sales))
dat_vk <- na.omit(dat_vk)

dat_vk_r <- cor(dat_vk$Sales_Dollars, dat_vk$city_sales)
cat("Correlation of avg Vodka sales between cities and zipcodes is:", dat_vk_r)
#####
```

```{r}
# Plot a couple to see what they look like

# Vodka
ggplot(dat_vk, aes(x=Sales_Dollars, y=city_sales)) +
  geom_point() +
  labs(title="Vodka avg City Sales vs avg Zipcode Sales",
       x="avg Zipcode Sales",
       y="avg City Sales") +
  geom_smooth(method = lm, se=FALSE)

# Whiskey
ggplot(dat_wh, aes(x=Sales_Dollars, y=city_sales)) +
  geom_point() +
  labs(title="Whisky avg City Sales vs avg Zipcode Sales",
       x="avg Zipcode Sales",
       y="avg City Sales") +
  geom_smooth(method = lm, se=FALSE)

# Brandy
ggplot(dat_br, aes(x=Sales_Dollars, y=city_sales)) +
  geom_point() +
  labs(title="Brandy avg City Sales vs avg Zipcode Sales",
       x="avg Zipcode Sales",
       y="avg City Sales") +
  geom_smooth(method = lm, se=FALSE)

# Gin
ggplot(dat_g, aes(x=Sales_Dollars, y=city_sales)) +
  geom_point() +
  labs(title="Gin avg City Sales vs avg Zipcode Sales",
       x="avg Zipcode Sales",
       y="avg City Sales") +
  geom_smooth(method = lm, se=FALSE)
```

We can see from the plots they are all very similar and don't show a very strong correlation. There is a correlation, but it is not very high. 


Performing analysis on liquor sales in Iowa across zip code, city, and county geographies in R and Tableau can provide valuable insights into sales patterns, consumer behavior, and market trends. However, both tools have their advantages and challenges in terms of data analysis.

Advantages of R:
R provides a wide range of statistical and data analysis tools, making it easy to process and analyze large datasets.
R allows for advanced data visualization and graphical representation, making it easier to identify patterns and trends in the data.
R is an open-source programming language, making it easy for us to share and collaborate on code and analysis.

Challenges of R:
R can be challenging to use for users without a programming background or experience with statistical analysis.
R requires more time and effort to learn and set up compared to other data analysis tools.
R is primarily used for statistical analysis and may not have as many features for data visualization as other tools like Tableau. We found it more difficult to represent visualizations in a customized manner in R, so we incorporated Tableau visulzations as well.

Advantages of Tableau:
Tableau provides an easy-to-use interface for data analysis and visualization, making it accessible to users without programming experience.
Tableau has a wide range of pre-built visualizations and templates, making it easy to create professional-looking reports and dashboards.
Tableau allows for interactive analysis, making it easier to explore the data and identify trends.
Challenges of Tableau:
Tableau can be limiting for advanced statistical analysis and modeling compared to R.
Tableau may not be ideal for analyzing large datasets, as it may become slow to work with.
In summary, R and Tableau both have their advantages and challenges for analyzing liquor sales in Iowa across zip code, city, and county geographies. R is ideal for advanced statistical analysis, while Tableau is useful for data visualization and analysis. A combination of both tools allowed us to perform our anlaysis and visualization for Iowa liquor sales data.

```

